TINET+TECS: Component-based TCP/IP Protocol Stack for Embedded Systems

### 2016-12-23 ISORC2017/paper.tex
Update paper.tex

% author names and affiliations
% use a multiple column layout for up to three different
% affiliations
\author{\IEEEauthorblockN{Takuro Yamamoto}
\IEEEauthorblockA{Graduate School of Engineering Science\\Osaka University}
\and
\IEEEauthorblockN{Takuma Hara}
\IEEEauthorblockA{}
\and
\IEEEauthorblockN{Takuya Ishikawa}
\IEEEauthorblockA{}
\and
\IEEEauthorblockN{Hiroshi Oyama}
\IEEEauthorblockA{OKUMA Corporation}
\and
\IEEEauthorblockN{Hiroaki Takada}
\IEEEauthorblockA{}
\and
\IEEEauthorblockN{Takuya Azumi}
\IEEEauthorblockA{Graduate School of Engineering Science\\Osaka University}
}

@@

% for over three affiliations, or if they all won't fit within the width
% of the page, use this alternative format:
% 
% \author{\IEEEauthorblockN{Michael Shell\IEEEauthorrefmark{1},
% Homer Simpson\IEEEauthorrefmark{2},
% James Kirk\IEEEauthorrefmark{3}, 
% Montgomery Scott\IEEEauthorrefmark{3} and
% Eldon Tyrell\IEEEauthorrefmark{4}}
% \IEEEauthorblockA{\IEEEauthorrefmark{1}School of Electrical and Computer Engineering\\
% Georgia Institute of Technology,
% Atlanta, Georgia 30332--0250\\ Email: see http://www.michaelshell.org/contact.html}
% \IEEEauthorblockA{\IEEEauthorrefmark{2}Twentieth Century Fox, Springfield, USA\\
% Email: homer@thesimpsons.com}
% \IEEEauthorblockA{\IEEEauthorrefmark{3}Starfleet Academy, San Francisco, California 96678-2391\\
% Telephone: (800) 555--1212, Fax: (888) 555--1212}
% \IEEEauthorblockA{\IEEEauthorrefmark{4}Tyrell Inc., 123 Replicant Street, Los Angeles, California 90210--4321}}

@@

Component-based development is an approach to improve software productivity.
Component-based development is a design technique that can be applied to reusable software development \cite{par:CBD}, such as TECS \cite{par:TECS}, AUTOSAR \cite{url:AUTOSAR}, and SaveCCM \cite{par:SAVEapproach}.
Component-based systems are flexible to software extension and specification changes.
In addition, individual component diagrams enable the visualization of an entire system.

In this paper, component-based TCP/IP protocol stack, i.e., componentized TINET, is proposed to improve the configurability and scalability of software.
TECS (TOPPERS Embedded Component System) \cite{par:TECS} is utilized to componentize TINET, because TECS is a component system suitable for embedded systems.
TECS supports static configuration, which statically defines component behaviors and interconnections, thus TECS can optimize the overhead of componentization.

@@

    \item {\bf Support legacy codes}\mbox{}\\
        TECS supports the adapter to call TECS functions from C codes, thus TINET+TECS can use an existing application.
    % \item {\bf Software visualization}

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=6.5cm,clip]{figure/SystemModel.pdf}
    \caption{System model}
    \label{fig:SystemModel}
\end{figure}

@@

@@

TINET runs as middleware on TOPPERS/ASP3 \cite{url:ASP3}, a realtime kernel.
Fig. \ref{fig:TINET_Hier} shows the hierarchy diagram of TINET and TOPPERS/ASP3.
TINET supports ITRON TCP/IP API such as {\it tcp\_snd\_buf}, {\it tcp\_rcv\_buf}, {\it udp\_snd\_buf}, and {\it udp\_rcv\_buf}.

\begin{enumerate}
    \item Minimum copy frequency
    \item Elimination of dynamic memory control
    \item Asynchronous interface
    \item Error detailed per API
\end{enumerate}

@@

\subsection{Component of protocol stack}

@@

TECS supports {\it Adapter} functionality which enables to call a function in TECS from C codes.
An adapter connects a TECS component, and links a C function to a TECS function shown as Fig. \ref{fig:TECS_Adapter}.
Software developers can utilize an existing application for TECS owing to the adapter.

>>>>

% author names and affiliations
% use a multiple column layout for up to three different
% affiliations
\author{
\IEEEauthorblockN{Takuro Yamamoto}
\IEEEauthorblockA{Graduate School of Engineering Science\\Osaka University}
\and
\IEEEauthorblockN{Takuma Hara}
\IEEEauthorblockA{Graduate School of Information Science\\Nagoya University}
\and
\IEEEauthorblockN{Takuya Ishikawa}
\IEEEauthorblockA{Graduate School of Information Science\\Nagoya University}
\and
\IEEEauthorblockN{Hiroshi Oyama}
\IEEEauthorblockA{OKUMA Corporation}
\and
\IEEEauthorblockN{Hiroaki Takada}
\IEEEauthorblockA{Graduate School of Information Science\\Nagoya University}
\and
\IEEEauthorblockN{Takuya Azumi}
\IEEEauthorblockA{Graduate School of Engineering Science\\Osaka University}
}

@@

% for over three affiliations, or if they all won't fit within the width
% of the page, use this alternative format:
% 
% \author{
% \IEEEauthorblockN{
% Takuro Yamamoto\IEEEauthorrefmark{1},
% Takuma Hara\IEEEauthorrefmark{2},
% Takuya Ishikawa\IEEEauthorrefmark{2}, 
% Hiroshi Oyama\IEEEauthorrefmark{3},
% Hiroaki Takada\IEEEauthorrefmark{2} and
% Takuya Azumi\IEEEauthorrefmark{1}}
% \IEEEauthorblockA{\IEEEauthorrefmark{1}Graduate School of Engineering Science, Osaka University}
% \IEEEauthorblockA{\IEEEauthorrefmark{2}Graduate School of Information Science, Nagoya University}
% \IEEEauthorblockA{\IEEEauthorrefmark{3}OKUMA Corporation}
% }

@@

Component-based development is an approach to improve software productivity.
Component-based development is a design technique that can be applied to reusable software development \cite{par:Crnkovic}\cite{par:CBD}, such as TECS \cite{par:TECS}, AUTOSAR \cite{url:AUTOSAR}, and SaveCCM \cite{par:SAVEapproach}.
Component-based systems are flexible to software extension and specification changes.
In addition, individual component diagrams enable the visualization of an entire system.

In this paper, component-based TCP/IP protocol stack, i.e., componentized TINET, is proposed to improve the configurability and scalability of software.
TECS (TOPPERS Embedded Component System) \cite{par:TECS} is utilized to componentize TINET, because TECS is a component system suitable for embedded systems.
TECS supports static configuration, which statically defines component behaviors and interconnections, thus TECS can optimize the overhead of componentization.
This paper evaluates the overheads of execution time and memory consumption and amount of code line change for adding/removing the functionalities, which demonstrates TINET+TECS can improve the configurability with small overheads.

@@

    \item {\bf Support legacy codes}\mbox{}\\
        TECS supports the adapter to call TECS functions from existing C codes, thus TINET+TECS can be applied to an existing application.
    % \item {\bf Software visualization}

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=6.5cm,clip]{figure/SystemModel.pdf}
    \caption{System model}
    \label{fig:System Model}
\end{figure}

@@

\begin{itemize}
    \item Minimum copy frequency
    \item Elimination of dynamic memory control
    \item Asynchronous interface
    \item Error detailed per API
\end{itemize}

@@

TINET runs as middleware on TOPPERS/ASP3 \cite{url:ASP3}, which is a realtime kernel based on $\mu$ITRON \cite{par:microITRON}.
TINET also supports other RTOSs such as TOPPERS/ASP and TOPPERS/JSP because TINET is compatible with TOPPERS RTOS.
Fig. \ref{fig:TINET_Hier} shows the hierarchy diagram of TINET and TOPPERS/ASP3.
% TINET supports ITRON TCP/IP API such as {\it tcp\_snd\_buf}, {\it tcp\_rcv\_buf}, {\it udp\_snd\_buf}, and {\it udp\_rcv\_buf}.
Users transmit and receive the data using a Communication End Point (CEP) which is an interface like a socket.
In transmission process, headers are attached to the data body passed to the CEP at each protocol layer, and the data is transmitted from the network device.
In reception process, headers of the data body received in the network device are analyzed at each protocol layer, and the data is passed to the CEP.

In TINET, the number of the data copy between each protocol layers is minimized.
A TCP/IP protocol stack for general computers has large overheads of execution time and memory consumption because the data is copied at each protocol layers.
To solve the problem, TINET does pass the pointer of the data buffer between each protocol layers, not perform data copy.

@@

TINET+TECS, the proposed componentized TCP/IP protocol stack, consists of some TECS components.
This section describes the components with component diagrams.
In addition, TECS functionalities applied to the proposed system such as {\it send}/{\it receive} specifier and adapter are explained.

\subsection{Components of protocol stack}

@@

TECS supports {\it Adapter} functionality which enables to call a function in TECS from existing C codes.
An adapter connects a TECS component, and links a C function to a TECS function shown as Fig. \ref{fig:TECS_Adapter}.
Software developers can utilize an existing application for TECS owing to the adapter.
